\documentclass[22pt, a4paper]{article}
\usepackage{epsfig}
\hbadness 5000

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex}
\textwidth 17cm
\textheight 24.5cm
\oddsidemargin 0.0cm
\evensidemargin 0.0cm

\begin{document}

\begin{Large}

\section{Design Decision Summary}

\subsection{Introduction}
\subsubsection{Document Aim}

To record details of design decisions in a single document.

\subsubsection{Project Design Aims}
The design aims of the project are:
\begin{enumerate}
\item Satisfy the functional requirements
	\begin{itemize}
	\item create a consistent and complete design based upon the
	requirements specified in the SRS.
	\item document any design decisions related to satisfying the
	functional requirements
	\end{itemize}
\item Satisfy the non-functional requirements.  Ensure that the following
quality attributes are satisfied: \\
{\bf Usability:} specific processes will be used to test the system is
usable.  Because our project is aimed at novice users this is the most
important quality attribute. \\
{\bf Performance:} in order to achieve the performance required we will
perform some tests and build some prototypes. \\
\end{enumerate}

\subsubsection{Executive Summary}
So far we have made design decisions about all of our functional
requirements.  Of non-functional we have only made choices for usability.

\pagebreak

\subsection{Functional Requirements}

\subsubsection{Database backend functionality}
For a more detailed description of each functional requirement please refer
to section 1 of the SRS.
\begin{enumerate}
\item
{\bf Activity: } Nadia did research on {\bf Date:} 6/4/01 \\
{\bf SRS items:} 1.1.1 through 1.1.25. \\
{\bf Aim:} Investigate various database technologies to check what
functionality they provide and ensure that the database interaction we have
in the SRS can be achieved.  Specifically looked at mySQL, MS-ACCESS and
Ingres.  (See minutes of team meeting on 4/4/01 online or in the
repository).  \\
{\bf Tradeoffs:} All of the the database alternatives have the
functionality we required (according to the documentation).  Ingres is
only supported on UNIX systems, MS-ACCESS on Windows and mySQL on Linux and
Windows.  Only mySQL is free.  Our clients wants something that is free,
although if the functionality is not there then we will select another
database technology.  Our client only has experience with MS-ACCESS. \\
{\bf Result:} I built a test mySQL database (see prototypes directory under
CVS).  I then performed all the database interactions listed in 1.1.1
through 1.1.25 on this test database.  mySQL will satisfy most of our
requirements.  This will require additional documentation and training
material for the client but we could create an "MS-like" interface.
\end{enumerate}

\subsubsection{Statistical functionality}
For a more detailed description of each functional requirement please refer
to section 2 of the SRS.
\begin{enumerate}
\item
{\bf Activity:} Deepak researched languages for implementation to aid in
bottom up design process on {\bf Date:} 6/4/01 \\
{\bf SRS items:} 2.1.1 through 2.1.13. \\
{\bf Aim:} Investigate various languages to implement statistical functions
listed in SRS items.  The options that the team has brainstormed are C, C++
and Java. \\
{\bf Tradeoffs:} There are free statistical libraries available for each
language.  This allows us a bit of flexibility for other design decisions.\\ 
{\bf Result:} I read documentation on each library and checked that they
satisfy the SRS items.  We can use any of the libraries for our project.
\end{enumerate}

\pagebreak

\subsection{Non-Functional Requirements}

Design decisions for each section of the functional requirements in the SRS.

\subsubsection{Usability}
For a more detailed description of the non-functional requirements
associated with usability see section 7 of the SRS. \\
\begin{enumerate}
\item
{\bf Activity:} Chuen created a paper prototype on {\bf Date:} 6/4/01 \\
{\bf SRS items:} 7.1.1 through 7.1.8. \\
{\bf Aim:} Create a basic paper prototype of the user interface to show the
client.  Use feedback from the client to refine the interface. \\
{\bf Result:} Created prototype.  These are labelled "1st Draft UI" in
design notebook/folder. \\
\item
{\bf Activity:} Ko-Chen demonstrated paper prototype to client on {\bf
Date:} 11/4/01 \\
{\bf SRS items:} 7.1.1 through 7.1.8. \\
{\bf Aim:} Gather feedback on the design of user interface. \\
{\bf Result:} Ammended paper prototype.  These are labelled "2nd Draft UI"
in design notebook/folder. \\
\end{enumerate}

\end{Large}
\end{document}
